---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# teref

<!-- badges: start -->
<!-- badges: end -->

The goal of teref is to provide certain reference tables, such as showing the correspondence between country and city names and codes across different databases and sources. This package contains three reference tables:
* __ctry_code_book:__ Country names and codes across databases. 
* __city_code_book:__ City names and codes across databases.
* __var_code_book_oegtc:__ Variable codes and descriptions to use with the Global City Travel database.

## Installation

You can install the package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TourismEconomics/teref")
```

## Organization
The tables, or code books, are stored as Rdata files in the "data" directory. 


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(teref)
## basic example code
```

